Analyse from review

### 2021-05-11 manuscript/bef_stability/appendixB.Rmd
Add trophic synchrony figure

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the links 
of the Structural Equation Models associated with the references supporting the links.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & sign & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

```{r hist-sem-data, cache = FALSE, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  labs(y = "Values", x = "Frequency") +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r sensitivity, cache = TRUE, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
library(furrr)

@@

```{r}
sens_cap <- paste0(
  "Sensivity analysis of the Structural Equation models for total biomass
  and its temporal stability."," The Constant dataset is the one keeping only the
  sites that does not show a clear temporal trend of community biomass; ", "Constant/
    without holes dataset kept only the constant sites plus the ones that had no
  holes in their sampling period; ", "Complete is the dataset containing all the
  sites that have been followed ten years or more;", " Without holes dataset is
  the complete dataset but containing only the sites that had no holes in their sampling period."
)
```

```{r, fig.height = 8, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))

@@

>>>>

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the links 
of the Structural Equation Models associated with the references supporting the links.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & Sign & References\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

```{r hist-sem-data, cache = FALSE, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  labs(y = "Frequency", x = "Values") +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r sensitivity, cache = TRUE, message = FALSE, fig.dim = c(10.5, 7), fig.cap = "Sensivity analysis with different dataset"}
library(furrr)

@@

```{r}
sens_cap <- paste0(
  "Sensivity analysis of the structural equation models for total biomass
  and its temporal stability."," The Constant dataset is the one keeping only the
  sites that does not show a clear temporal trend of community biomass; ", "Constant/
    without holes dataset kept only the constant sites plus the ones that had no
  holes in their sampling period; ", "Complete is the dataset containing all the
  sites that have been followed ten years or more;", " Without holes dataset is
  the complete dataset but containing only the sites that had no holes in their sampling period."
)
```

```{r, fig.height = 7, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))

@@

```{r}
sync_cap <- paste0(
  "Synchrony between trophic species pairs that are trophically linked or not.
  There is one point by trophic species pair and by site. The figure shows that
  the trophic species pairs that are trophically linked are more synchronous
  than the ones that are not trophically linked. Please see the definition of
  synchrony in the methods of the main text.") 
```

```{r, fig.cap=sync_cap}
knitr::include_graphics(mypath("manuscript", "bef_stability", "result", "synchrony_species_pairs.png"))
```

### 2021-05-11 manuscript/bef_stability/review_analysis.Rmd
Add trophic synchrony figure

```{r}
sync_pred <- sync_pair_int2 %>%
  ggplot(aes(y = sync, x = as.factor(interact))) +
  geom_boxplot() +
  labs(y = "Synchrony", x = "Species pairs in interaction", fill = "Cannibalism")
```

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "synchrony_species_pairs.png"),
    plot = sync_pred,
    base_height = 2.5, base_asp = 1.2#1.618 
    )
```

>>>>

```{r}
sync_pred <- sync_pair_int2 %>%
  mutate(interact = ifelse(interact, "Trophically linked", "Non trophically
      linked")) %>%
  ggplot(aes(y = sync, x = as.factor(interact))) +
  geom_boxplot() +
  labs(y = "Synchrony", x = " Trophic interactions betweem trophic species pairs", fill = "Cannibalism")
```

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "synchrony_species_pairs.png"),
    plot = sync_pred,
    base_height = 4.2, base_asp = 1.2#1.618 
    )
```
